# Continuous Integration (CI) {#ci}

## What is CI?
Work in progress.

If you know that you want Travis CI to skip a build (e.g., you’ve just edited the ReadMe file), include [ci skip] or [skip ci] anywhere in the commit message.

You can skip to `build` in Travis CI by putting keywords `[skip ci]` or `[ci skip]` in your commit messages. This can be used when doing minor changes such as fixing a typo in documentation,etc.

### tic

#### Installation with R Studio.

`remotes::install_github("ropensci/tic")`


then  A `GITHUB_PAT` needs to be set to create the
  SSH key pair required for deployment on
  GitHub Actions. Please call
  `usethis::browse_github_pat()`, follow the
  instructions and then call `use_tic()`
  again.
  
run `usethis::browse_github_pat()` This will open your github tokens page,may ask for your password. 
Generate the token with default settings provided and copy the token.
Now run `usethis::edit_r_environ()`. This will open `.Renviron` file of your project and 
now write `GITHUB_PAT=you_token_key_here`. Make sure you add an empty new line below that line. Save the file. Restart R for changes to take place.


#### for new user of tic 

Run `tic::use_tic()`

If you already use tic and want to configure a new CI provider do the following

#### For GitHub Actions 
```{r}
tic::use_ghactions_deploy() # (optional for deployment)
tic::use_ghactions_yml() # optional: Change `type` arg to your liking
cat(tic::use_tic_r("package", deploy_on = "ghactions"))
```

```{r}
# (all of the above in one call)
tic::use_tic(wizard = FALSE, linux = "ghactions", mac = "ghactions",
windows = "ghactions", matrix = "ghactions", deploy = "ghactions")
tic::use_tic_badge("ghactions")
tic::use_update_tic()
```

You can use `usethis::edit_file('.github/workflows/tic.yml')` to edit the tic file and comment out platforms.
## Why we need it?

## `bdverse` CI strategy

# GitHub Actions {#github-actions}
`r emo::ji("construction")` **Under Construction** `r emo::ji("construction")`

## File Sync System {#file-sync}
https://github.com/marketplace/actions/file-sync
