#  (PART) Documentation {-}
 <!-- PART 3: Documentation -->
 
 
# Centralized Documentation Scheme {#doc-system}

`r emo::ji("construction")` **Under Construction** `r emo::ji("construction")`

## The main idea

```{r setup, include=FALSE}

import_example <- function(file, lang = xfun::file_ext(file)) {
  x = xfun::read_utf8(file.path("inst", file))
  lang = tolower(lang)
  if (nchar(lang) > 1) {
    lang = sub('^r', '', lang)
    if (lang == 'nw') lang = 'tex'
  }
  knitr::asis_output(paste(c(sprintf("````%s", lang), x, "````"), collapse = '\n'))
}
```

## The implementation

### Source Rmd files

Pkg Info specifically build for a package, here is a generic example:

```{r echo=FALSE}
# a single file
xfun::embed_file('inst/pkg_info.Rmd')
```

`r import_example('pkg_info.Rmd')`

[Rmd templates](#rmd-templates)
  
### Client Rmd files:

- Pkg README.Rmd
- Pkg Rmd file in the user guide
- Pkg Rmd file in the dev guide
- Pkg Rmd file in the website

A README example:
`r import_example('test-muli-RMD.Rmd')`

## Centralized reposotoiers

### bdtemplates

#### CI templates

#### .gitignore & .Rbuildignore

#### Rmd templates {#rmd-templates}
- Pkg info
- Pkg badges
- Pkg CI table

### Graphics

```{=html}
<div class="github-card" data-github="bd-r/bdgraphics" data-width="700" data-height="250" data-theme="default"></div>
<script src="//cdn.jsdelivr.net/github-cards/latest/widget.js"></script>
```
For more details [see bdgraphics (under the Graphics section)](#bdgraphics).



# User Guide {#user-guide}



# Website {#website}



# Pkg README file {#readme}



# Dev Guide {#dev-guide}


# Papers {#papers}



# Graphics {#graphics}

`r emo::ji("construction")` **Under Construction** `r emo::ji("construction")`

## Package color

```{=html}
<!-- Coolors Palette Widget -->
      <script src="https://coolors.co/palette-widget/widget.js"></script>
      <script data-id="06728234961140218">new CoolorsPaletteWidget("06728234961140218", ["265b6d","785549","4bae4d","37a5dd","ef4538","f7941d","6f3f98","939598"]); </script>
```

```{r, echo = FALSE, fig.cap="`bdverse` package"}
knitr::include_graphics("https://raw.githubusercontent.com/bd-R/bdgraphics/master/arc/bdverse/arc_bdverse_pkgs.svg")
```

### Retrieving pkg color

```{r}
# Data is stored in `bdutilities::bdverse_core_pkgs$pkg_color`
knitr::kable(bdutilities::bdverse_core_pkgs)
```

## bdgraphics {#bdgraphics}


```{=html}
<div class="github-card" data-github="bd-r/bdgraphics" data-width="700" data-height="250" data-theme="default"></div>
<script src="//cdn.jsdelivr.net/github-cards/latest/widget.js"></script>
```
<!-- [![bdgraphics](https://github-readme-stats.vercel.app/api/pin/?username=bd-R&repo=bdgraphics&show_owner=true)](https://github.com/bd-R/bdgraphics) -->