# `bddwc` {#bddwc}

`r emo::ji("construction")` **Under Construction** `r emo::ji("construction")`

## Pkg Info:

Title:

`r packageDescription("bdDwC")$Title`

Description:

`r packageDescription("bdDwC")$Description`

  
## Pkg Architecture

### Overview

```{r, echo = FALSE, fig.cap="bddwc overview"}
knitr::include_graphics("https://raw.githubusercontent.com/bd-R/bdgraphics/master/arc/bddwc/arc_bddwc.svg")
```

### R functions dependency & information 

```{r echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
source('inst/net_code_tables.R')
fun_tbl <- code_net(repo = 'bd-R/bdDwC', direction = "RL")
fun_tbl[[1]]
fun_tbl[[2]]
```

### Dependencies

<!-- # ```{r echo=FALSE, error=FALSE, message=FALSE, warning=FALSE} -->
<!-- # library(pkgnet) -->
<!-- #  -->
<!-- # pkgnet:::silence_logger() -->
<!-- #  -->
<!-- # reporters <- list(DependencyReporter$new()) -->
<!-- #  -->
<!-- # reporters <- lapply( -->
<!-- #           X = reporters -->
<!-- #           , FUN = function(reporter){ -->
<!-- #               reporter$set_package(pkg_name = "bdDwC") -->
<!-- #               return(reporter$nodes) -->
<!-- #           } -->
<!-- #       ) -->
<!-- #  -->
<!-- # DT::datatable(data = reporters$nodes, -->
<!-- #               escape = FALSE, -->
<!-- #               options = list("pageLength" = 30, -->
<!-- #                              order = list(list(4, 'desc')))) -->
<!-- #  -->
<!-- # ``` -->


### Testing




# `bddwc.app` {#bddwc.app}

`r emo::ji("construction")` **Under Construction** `r emo::ji("construction")`


# `bdchecks` {#bdchecks}
`r emo::ji("construction")` **Under Construction** `r emo::ji("construction")`



# `bdchecks.app` {#bdchecks.app}
`r emo::ji("construction")` **Under Construction** `r emo::ji("construction")`


# `bdclean` {#bdclean.app}
`r emo::ji("construction")` **Under Construction** `r emo::ji("construction")`


# Pkgs Under Construction

## bdvis

## bddashboard
https://github.com/rahulchauhan049/dashboard.experiment

## bdtools